Deep Reinforcement Learning for Conservation Decisions

### 2021-06-13 manuscript/manuscript.Rmd
journal submission formatting

keywords:
  - Reinforcement Learning
  - Conservation
  - Machine Learning
  - Artificial Intelligence
  - Tipping points
bibliography: references.bib
nocite: |
    @A2C, @trpo, @ddpg, @TD3, @impala
header-includes:
  - \usepackage{amsmath}
  - \usepackage{amssymb}
output: 
  rticles::arxiv_article:
    keep_tex: true
  word_document: default
editor_options: 
  markdown: 
    wrap: sentence
---

>>>>

keywords:
  - Reinforcement Learning
  - Conservation
  - Machine Learning
  - Artificial Intelligence
  - Tipping points
bibliography: references.bib
nocite: |
    @A2C, @trpo, @ddpg, @TD3, @impala
header-includes:
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \usepackage{lineno}
  - \usepackage{endfloat}
  - \linenumbers

output: 
  rticles::arxiv_article:
    keep_tex: true
  word_document: default
editor_options: 
  markdown: 
    wrap: sentence
---

Statement of Authorship:  ML and CB developed the code and wrote the manuscript with support from KEAN and MSC.

Data Accessibility Statement: No new empirical data were used in this analysis. Processed forms of public data used in this analysis, simulated data, and code are provided at <https://github.com/boettiger-lab/rl-intro>, archived on Zenodo Data Archive under series-DOI: <https://doi.org/10.5281/zenodo.4940139>.
